
\documentclass{article}

\usepackage[margin=1in]{geometry}

\begin{document}
    \section{Introduction}
    \section{Data}
    \section{Methods}
        \subsection{Probability model for runner outcomes}
            \subsubsection{Linear mixed-effects regression}
        \subsection{The baseball inning as a Markov decision process}
            \subsubsection{The single-agent model}
            \subsubsection{The two-agent model}
            \subsubsection{Policy iteration}
    \section{Results}
        \subsection{Runner outcome probabilities given lead distance}
            \begin{itemize}
                \item What is the relationship between lead distance and:
                \begin{itemize}
                    \item the probability of a pickoff attempt,
                    \item the success probability of a pickoff attempt,
                    \item the success probability of a stolen base attempt?
                \end{itemize}
            \end{itemize}
        \subsection{Optimal lead distance under current conditions}
            \begin{itemize}
                \item What is the optimal lead distance for the average runner against an average battery, as a function of disengagements?
                \item How does optimal lead distance change for 10$^{th}$-/90$^{th}$-percentile runner?
                How does optimal lead distance change for 10$^{th}$-/90$^{th}$-percentile battery?
                \item How many more runs could an offense expect to score (in the current environment) if they successfully implemented the optimal policy?
            \end{itemize}
        \subsection{Game theoretic equilibrium}
            \begin{itemize}
                \item How much more frequently does our model think pitchers should be attempting pickoffs? Under the game theoretic equilibrium, how frequently would pitchers be attempting pickoffs?
                \item Under the game theoretic equilibrium, what is the optimal lead distance for an average runner against an average battery, given disengagements?
                \item Relative to current conditions, would the game theoretic equilibrium favor offense or defense, and by how much?
            \end{itemize}
    \section{Discussion}
\end{document}
